\setcounter{section}{-1}
\section{Introduction}

	Python is a computer programming language designed for general-purpose use and can be found in use almost everywhere. Python was designed to be easy to read and write, making it the perfect language to start off with!

	Python has been around since 1991 and grew to be popular in 2003, where it was ranked in the top ten most popular programming languages (and it's still there!). It was the programming language of the year in 2007 and 2010 and even comes pre-installed on your Pi!

	%Difficulty
	This is an intermediate workshop, it will help to have some previous experience with Python.

	\subsection*{How to use these booklets}

		\input{McrRaspJam/Common/introduction/howto}

		%Code Listings
		\input{McrRaspJam/Common/introduction/listingcode}
		\input{McrRaspJam/Common/introduction/aside}

		%\input{McrRaspJam/Common/introduction/downloadlocation}

	\subsection*{What you'll need}

		For this workshop, you'll just need a working Raspberry Pi running a Linux operating system like Raspbian with Python installed. Luckily for us, Raspbian (and many other Linux distributions) include Python right out of the box.

	\subsection*{Everything else}

		%Aknowledgements
		\ifprint\else These booklets were created using \textrm{\LaTeX}, an advanced typesetting system used for several sorts of books, academic reports and letters. \fi

		%License spiel
		To allow modification and redistribution of these booklets, they are distributed under the \hbox{CC BY-SA 4.0} License.
		Latex source documents are available at \url{http://github.com/McrRaspJam/booklet-workshops}
