\setcounter{section}{-1}
\section{Introduction}
	
	On a Linux computer the desktop only scratches the surface of the programs and functionality available. Linux users often access these additional features through a terminal window, using the Command Line Interface (\textbf{CLI}), a non-graphical user interface.
	
	For many tasks, creative use of command-line commands is much faster than their GUI counterparts, especially in bulk tasks.	We'll only be able to take a look at the very basics today, but Linux geeks swear by the fact that each new trick they learn in the CLI allows them to save a little more time when using their computer.

	%Difficulty
	This is an introductory workshop. Once you're familiar with using your Pi on the desktop, you should be ready to attempt this workshop.
		
	\subsection*{How to use these booklets}

		\input{McrRaspJam/common/introduction/howto}
		
		%Code Listings
		\input{McrRaspJam/012_CLI/0_introduction/listingterminal}
		\input{McrRaspJam/012_CLI/0_introduction/aside}
		
		%\input{McrRaspJam/Common/introduction/downloadlocation}
	
	\subsection*{What you'll need}
		
		For this workshop, you'll just need a working Raspberry Pi running a Linux operating system like Raspbian.
		
	\subsection*{Everything else}
		
		%Aknowledgements
		\ifprint\else These booklets were created using {\fontfamily{rfdefault}\selectfont \LaTeX}, an advanced typesetting system used for several sorts of books, academic reports and letters. \fi
		
		%License spiel
		To allow modification and redistribution of these booklets, they are distributed under the \hbox{CC BY-SA 4.0} License. LaTeX source documents are available at \mbox{\href{http://github.com/McrRaspJam/booklet-workshops}{github.com/McrRaspJam/booklet-workshops}}
		
		If you get stuck, find errors or have feedback about these booklets, please email me at:
		\mbox{\url{jam@jackjkelly.com}\label{email}}