\section{The Ultimate Command of Destruction}

	The Linux command line places a lot of trust in you. As far as it's aware, you're somebody who knows what your doing. If you don't know what you're doing, be careful.
	
	We're going to have a look at some useful features of the command line, and see what happens when you combine them incorrectly.
		
	\subsection*{-f}
	
		\textbf{-f} stands for force, and on a command like rm skips any warning messages that would usually be created.
		
		if we were trying to delete 1000 files which were set as read-only, we would usually have to answer a yes/no check on every single file. -f will stop that from happening, so the command would finish instantly.
	
	\subsection*{sudo}
	
		\textbf{sudo} stands for superuser do. Any time we want to complete a command that requires a high level of authority, such as modifying the read-only files mentioned above, we run that command as a superuser using sudo.
		
		This command effectively means ``I know what I'm doing'', so make sure you do!
	
	\subsection*{Wildcards}
	
		In the CLI, the asterisk character \textbf{*} is used as a wildcard. If we wanted to delete all the .txt files from a directory filled with thousands of different files, we could find each one and manually type in
	
		\begin{lstlisting}[style=Terminal]
$ rm file23of9000.txt
$ rm file72of9000.txt
$ rm file73of9000.txt
$ rm file79of9000.txt
...
		\end{lstlisting}

		or, using a wildcard, we can search for a partial name. Entering:
		\begin{lstlisting}[style=Terminal]
$ rm *.txt
		\end{lstlisting}

		would delete all of the files ending in `.txt', just like we wanted. Likewise, to delete all the files beginning with January, we could do:
		\begin{lstlisting}[style=Terminal]1
$ rm january*
		\end{lstlisting}
	
		But what if you tried a command such as `rm *'? By default it would stop within the current folder, and possibly the sub folders, but what if we accidentally told it not to?
	
	\subsection{Making the wrong combination}
	
	The truly scary thing about the ultimate command of destruction is how inconspicuous it looks.
	
		\begin{lstlisting}[style=Terminal]
$ sudo rm -rf /
		\end{lstlisting}

		Let's break the command down.
		
		rm is our standard remove file function. To it, we have supplied the flags \textbf{-rf}. -f means we know what we're doing, and -r means it will start at one point and work through every subdirectory it finds.
		
		This is fine if we're trying to delete a Java Project folder, or a collection of cat pictures, but what directory have we supplied?
		
		\textbf{/} is the root directory, the directory under which every single file on our computer is contained.
		
		The Operating system would have stopped you, but we've ran it under \textbf{sudo}, so the computer's convinced we done this intentionally.
		
		And now (if you're happy to wipe whatever SD card you're running on) you can try it on your Raspberry Pi.\footnote{A feature of modern Linux distributions, at this point the program throws one last warning at you to try and stop you.
			
		If you're really \textit{really} happy to lose all of your files, just add the flag it tells you to, and it \textit{will} finally run your command.} I'd recommend adding the flag -v for dramatic effect, which will display the files as they're being deleted.
	
		\begin{lstlisting}[style=Terminal]
$ sudo rm -rfv /
		\end{lstlisting}

\section{The End}

	Whilst it certainly is for your Raspberry Pi (until you reinstall NOOBS, that is), I thought I'd leave you with one story about accidental misuse of rm.
	
	This story about a quite famous film company is available as a video at \url{https://youtu.be/8dhp_20j0Ys}, and a text article is available at \url{http://bit.ly/2jgR3nC}.
	
	\iftoggle{isPRINT}{}{
		Try not to be too intimidated by what you've just accomplished Getting you to destroy your Pi in a single command wasn't meant to scare you away from using the command line, just to show you the power that it gifts you.
	}