\setcounter{section}{-1}
\section{Introduction}

	Last month in \href{http://mcrraspjam.org.uk/workshop-15-gpio-zero/}{workshop 15}, we \textit{encoded} a message in Morse code, a method that makes it simpler to transmit written language through rudimentary means, such as a spotlight, or a pulse in an electrical wire.
	
	We also often use the word \textit{code} to refer to an encrypted \textbf{cipher}. A different type of encoding, when we encode a message in a cipher, we attempt to make the message difficult---or ideally impossible--- for an outsider to read.
	
	Today, we'll have a go at encoding, decoding and cracking some famous ciphers of the classical era using Python programs, as well as taking a look at more modern ciphers and some of the cryptography tools available to us as users of Linux on the Raspberry Pi.
	
	
	%Difficulty
	This is an introductory workshop, all of the Python concepts will be covered from scratch.
		
	\subsection*{How to use these booklets}

	\input{McrRaspJam/common/introduction/howto}
	
	%Code Listings
	\input{McrRaspJam/015_GPIOZero/0_introduction/listingcode}
	\input{McrRaspJam/015_GPIOZero/0_introduction/aside}
	
	\ifprint\else
		\subsection*{What you'll need}
		All of the software you for this workshop is pre-installed on recent versions of Raspbian.
	\fi
		
	\subsection*{Everything else}
	
		% Aknowledgements
		These booklets were created using \textrm{\LaTeX}, an advanced typesetting system used for several sorts of books, academic reports and letters.
			
		\ifprint\else If you'd like to have a look at using LaTeX, We recommend looking at \TeX studio, which is available on most platforms, and also in the Raspbian repository. \fi
		
		% License spiel
		To allow modification and redistribution of these booklets, they are distributed under the \hbox{CC BY-SA 4.0} License.
		Latex source documents are available at \url{http://github.com/McrRaspJam/booklet-workshops}
		
		If you get stuck, find errors or have feedback about these booklets, please email me at:
		\href{mailto:jam@jackjkelly.com}{\texttt{jam@jackjkelly.com}}