\setcounter{section}{-1}
\section{Introduction}
	
	Object-oriented programming is a different way to represent complex concepts than the traditional programming methods. Today we'll take a look at what objects are using the Java programming language.
	
	Then, we'll use objects to create characters for a computerised tabletop role-playing game.

	%Difficulty
	This is an intermediate workshop, that builds upon a familiar knowledge of a text-based programming language like Python.
		
	\subsection*{How to use these Booklets}

	\input{McrRaspJam/common/introduction/howto}
	
	%Code Listings
	\input{McrRaspJam/013_Objects/0_introduction/listingcode}
	\input{McrRaspJam/013_Objects/0_introduction/listingterminal}
	\input{McrRaspJam/013_Objects/0_introduction/aside}
		
	%Aknowledgements
	These booklets were created using {\fontfamily{rfdefault}\selectfont \LaTeX}, an advanced typesetting system used for several sorts of books, academic reports and letters.
		
	%License spiel
	To allow modification and redistribution of these booklets, they are distributed under the \hbox{CC BY-SA 4.0} License. LaTeX source documents are available at \mbox{\href{http://github.com/McrRaspJam/booklet-workshops}{github.com/McrRaspJam/booklet-workshops}}
	
	%\input{McrRaspJam/Common/introduction/downloadlocation}
	
	\subsection*{What you'll need}
		
		We'll be using Java for this workshop, which is installed by default in Raspbian.
		
	\subsection*{Questions?}
		If you get stuck, find errors or have feedback about these booklets, please email me at:
		\mbox{\url{jam@jackjkelly.com}\label{email}}