\setcounter{section}{-1}
\section{Introduction}
	
	%Background
	The \textit{Sense HAT} is an add-on board for the Raspberry Pi designed especially for the Astro Pi mission, which now sent several Raspberry Pi's into orbit onboard the International Space Station.
	
	The Sense HAT is a single board which adds a variety of input sensors, as well as a programmable 8x8 LED matrix to the Raspberry Pi.
	
	%Workshop Description	
	This workshop will teach you how to write Python programs to access the features of the Sense HAT, using the Python API that is installed in Raspbian.

	%Difficulty
	This is an introductory workshop, all of the Python concepts will be taught from scratch.
		
	\subsection*{How to use these booklets}
	
		\input{McrRaspJam/common/introduction/howto}
		
		%Code Listings
		\input{McrRaspJam/008_SenseHAT/0_introduction/listingcode}
		\input{McrRaspJam/008_SenseHAT/0_introduction/aside}
		
	\subsection*{Programming with Python}
	
		We'll be coding in Python for this workshop, and we'll be using a program called IDLE to write our programs.
		It is an `IDE', containing a text editor to write our programs, as well as a Python `Shell' where we will run them.
		
		To start IDLE\label{IDLE}, go to the main menu from the Raspberry Pi's desktop, then click \mbox{`Programming $\rightarrow$ Python 3'}. IDLE will start after a couple of seconds.
	
	\subsection*{Everything else}
	
		% Aknowledgements
		These booklets were created using \textrm{\LaTeX}, an advanced typesetting system used for several sorts of books, academic reports and letters.
		
		\ifprint\else If you'd like to have a look at using LaTeX, We recommend looking at \TeX studio, which is available on most platforms, and also in the Raspbian repository.\fi
		
		% License spiel
		To allow modification and redistribution of these booklets, they are distributed under the \hbox{CC BY-SA 4.0} License.
		Latex source documents are available at \url{http://github.com/McrRaspJam/booklet-workshops}
		
		If you get stuck, find errors or have feedback about these booklets, please email me at:
		\href{mailto:jam@jackjkelly.com}{\texttt{jam@jackjkelly.com}}