\setcounter{section}{-1}
\section{Introduction}

	If you've controlled electronics using the Raspberry Pi's GPIO before, you probably used a Python library called \textit{RPi.GPIO} to write your programs. GPIO Zero is an alternative GPIO library for Python, designed to be easier to use than RPi.GPIO, whilst having the same capabilities.

	Today, we'll learn how to create simple breadboard circuits using the Raspberry Pi's GPIO, then we'll write Python programs that control those circuits using the GPIO Zero library.

	%Difficulty
	This is an introductory workshop, for people who have tried basic programming in Python before.
		
	\subsection*{How to use these booklets}

	\input{McrRaspJam/common/introduction/howto}
	
	%Code Listings
	\input{McrRaspJam/015_GPIOZero/0_introduction/listingcode}
	\input{McrRaspJam/015_GPIOZero/0_introduction/aside}

		
	\subsection*{What you'll need}
	
	To create the circuits in this workshop, you will need:
	
	\begin{itemize}[nosep]
		\item A solderless breadboard and jumper wires
		\item Red, yellow and green LEDs
		\item A push-button tactile switch
		\item Suitable resistors for the LEDs and button
		\item A 3-5V \textbf{DC} piezo buzzer
	\end{itemize}
	
	\ifprint\else All of the software you for this workshop is pre-installed on recent versions of Raspbian. \fi
		
	\subsection*{Everything else}
	
		% Aknowledgements
		\ifprint\else
			These booklets were created using \textrm{\LaTeX}, an advanced typesetting system used for several sorts of books, academic reports and letters.
			
			If you'd like to have a look at using LaTeX, We recommend looking at \TeX studio, which is available on most platforms, and also in the Raspbian repository.
		\fi
		
		
		% License spiel
		To allow modification and redistribution of these booklets, they are distributed under the \hbox{CC BY-SA 4.0} License.
		Latex source documents are available at \url{http://github.com/McrRaspJam/booklet-workshops}
		
		If you get stuck, find errors or have feedback about these booklets, please email me at:
		\href{mailto:jam@jackjkelly.com}{\texttt{jam@jackjkelly.com}}